---
title: "GLOBAL MAMMALS DASHBOARD"
output:
  flexdashboard::flex_dashboard:
    theme: cerulean # can choose from: cosmo, bootstrap, cerulean, journal, flatly, readable, spacelab, united, lumen, paper, sandstone, simplex, yeti
    storyboard: true
runtime: shiny
---

```{r global, include=FALSE}
# STILL TO DO: MAKE IT LOAD FASTER

rm(list=ls())

### Load libraries -----
# Will automatically install any libraries it can't find
packages <- c("flexdashboard", "shiny", "knitr", "tidyverse", "magrittr", "leaflet", "RgoogleMaps", "shinyBS", "plotrix", "shinyjs", "cowplot")
package.check <- lapply(packages, FUN = function(x) {
  if (!require(x, character.only = TRUE)) {
    install.packages(x, dependencies = TRUE, repos = "http://cran.us.r-project.org")
    library(x, character.only = TRUE)
  }
})

opts_chunk$set(root.dir = getwd())

datMap <- read_csv("data/shiny_data2.csv")
Out_list <- reactiveValues(MammalsDat = datMap)
```

Learn about threats to mammals... {.storyboard}
=========================================
### Threats to mammals...

```{r plot1}
readRDS("shiny-figures_files/plot_byThreat.RDS")
```

***

Placeholder for longer descriptive text for the THREATS TO MAMMALS story panel...put longer commentary here

### Threats by family... 

```{r plot2}
readRDS("shiny-figures_files/plot_byFamily.RDS")
```

***

Placeholder for longer descriptive text for the THREATS BY FAMILY story panel...put longer commentary here

### Threats by continent... 

```{r plot3}
readRDS("shiny-figures_files/plot_byCont.RDS")
```

***

Placeholder for longer descriptive text for the THREATS BY CONTINENT story panel...put longer commentary here

### Threats by body mass... 

```{r plot4}
readRDS("shiny-figures_files/plot_byMass.RDS")
```

***

Placeholder for longer descriptive text for the THREATS BY MASS story panel...put longer commentary here

### Threats by home range... 

```{r plot5}
readRDS("shiny-figures_files/plot_byHR.RDS")
```

***

Placeholder for longer descriptive text for the THREATS BY HOME RANGE story panel...put longer commentary here

Explore maps...
====================================== 
Inputs {.sidebar data-width=250}
-------------------------------------
```{r maps_input}

radioButtons("sel_MapOrder",
            label = "Select a host order:",
            choices = c("ALL", "Artiodactyla", "Carnivora", "Primata", "Perissodactyla"),
            selected = "ALL")
    
radioButtons("sel_MapThreat", 
             label = "Choose a threat status:", 
             choiceNames = list("Least Concern", "Near Threatened", "Vulnerable", "Endangered", "Critically Endangered", "Extinct"), 
             choiceValues = list("0", "1", "2", "3", "4", "5"), #>>>>>>>>>>>> CHECK WHAT THESE NUMBERS MEAN
             selected = "0")

radioButtons("sel_MapContinent", 
             label = "Select a continent:", 
             choices = list("ALL", "Africa", "Asia", "Europe", "North America", "South America", "Australia"),
             selected = "ALL")

renderUI({
  if(!is.null(Out_list$MammalsDat) & !is.null(input$sel_MapOrder) & !is.null(input$sel_MapContinent) & !is.null(input$sel_MapThreat)) {
    
     mammals <- 
       ifelse(input$sel_MapContinent=="ALL", subset(Out_list$MammalsDat, Threat==as.numeric(input$sel_MapThreat)),
         subset(Out_list$MammalsDat, Threat==as.numeric(input$sel_MapThreat) & continent==input$sel_MapContinent))
     
     if(input$sel_MapOrder!="ALL") {mammals <- subset(mammals, order==input$sel_MapOrder)}
     
     mammalsNam <- unique(sort(mammals$hostName)) %>% unlist()
     
     selectInput("sel_MapSpecies",
                 label = "Select a species:",
                 choices = mammalsNam,
                 selected = mammalsNam[1])
    }
})

# renderUI({
#   if(!is.null(input$sel_MapPark) & !is.null(Out_list$CUPNbounds)) {
#     CUPNmapbounds_SP <- subset(Out_list$CUPNbounds, SubUnitLab==input$sel_MapPark)
# map_zoom <- min(MaxZoom(lonrange = range(CUPNmapbounds_SP$long), latrange = range(CUPNmapbounds_SP$lat)))
# 
#   sliderInput("sel_MapZoom", label = "Set map zoom (smaller = wider view):", min = map_zoom - 8, max = 17, value = map_zoom - 0.25, step = 0.25, ticks = FALSE, dragRange = FALSE, width = "85%")
#     }
#   })
```

Column
-------------------------------------
```{r maps}
# output$vegmap = renderLeaflet({
#   validate(need(!is.null(Out_list$CUPNbounds) & !is.null(Out_list$MapDat), message = FALSE))
#   Dat_df = Out_list$MapDat[[input$sel_MapMetric]]
#   if(input$sel_MapMetric == "OakHick") {
#     Dat_df = Out_list$OakHick[["OHfinal_df"]] %>%
#       dplyr::rename(Metric = MeanOSI) %>%
#       dplyr::mutate(Poptext = paste0(Plot, " (", Year, "):", "<br/>", Metric, " (95% CI ", Low95OSI, ", ", High95OSI, ")"))
#   }
#   if(input$sel_MapMetric == "HPExoticCov") {
#     Dat_df = subset(Dat_df, PlantName == input$sel_HPExotic)
#   }
#   
#   if(!is.null(input$sel_MapPark) & !is.null(input$sel_MapCycle) & !is.null(input$sel_MapMetric) & !is.null(input$sel_MapZoom)) {
#   
#   MapDat_df <- subset(Dat_df, SubPark==input$sel_MapPark & Cycle==input$sel_MapCycle)
#   
#   CUPNmapbounds_SP <- subset(Out_list$CUPNbounds, SubUnitLab==input$sel_MapPark)
#   map_center <- c(mean(c(min(CUPNmapbounds_SP$long), max(CUPNmapbounds_SP$long))), mean(c(min(CUPNmapbounds_SP$lat), max(CUPNmapbounds_SP$lat))))
# 
#   if(!is.null(MapDat_df)) {
#     basemap <- leaflet(data = MapDat_df, options = leafletOptions(zoomControl = FALSE, zoomSnap = 0.25)) %>%
#       addProviderTiles("Esri.WorldImagery") %>%
#       setView(lng = map_center[1], lat = map_center[2], zoom = input$sel_MapZoom)
#     
#     pieces <- unique(unlist(subset(Out_list$CUPNbounds, SubUnitLab==input$sel_MapPark, select = "piece")))
#     for (p in pieces) {
#       d <- subset(Out_list$CUPNbounds, SubUnitLab==input$sel_MapPark & piece==p)
#       basemap %<>%
#         addPolylines(lat = d$lat, lng = d$long, weight = 2, color = "yellow", opacity = 1)
#     }
# 
#     binvals <- switch(input$sel_MapMetric,
#         OakHick = c(xmin = 0, xmax = 2, xcut1 = 0.5, xcut2 = 1, xstep = 0.1, title = "Oak-Hickory OSI", rev = TRUE),
#         NativeRich = c(xmin = 0, xmax = 10*ceiling(max(Out_list$MapDat$NativeRich$Metric)/10), xcut1 = 40, xcut2 = 60, xstep = 2, title = "# native species", rev = TRUE),
#         ExoticRich = c(xmin = 0, xmax = 2*ceiling(max(Out_list$MapDat$ExoticRich$Metric)/2), xcut1 = 4, xcut2 = 8, xstep = 2, title = "# exotic species", rev = FALSE),
#         ExoticCov = c(xmin = 0, xmax = 100, xcut1 = 5, xcut2 = 15, xstep = 5, title = "% exotic cover", rev = FALSE),
#         HPExoticCov = c(xmin = 0, xmax = 100, xcut1 = 2, xcut2 = 4, xstep = 2, title = "% species cover", rev = FALSE))
#     
#     ColorScheme <- switch(input$sel_ColorScheme, WBO = c("#FFFFFF", "#9ad0f3", "#e79f00"), WOR = c("#FFFFFF", "#e79f00", "#D55E00"))
#     
#     pal_bins <- colorBin(ColorScheme, bins = c(as.numeric(binvals["xmin"]), input$sel_MapScore[1], input$sel_MapScore[2], as.numeric(binvals["xmax"])), reverse = as.logical(binvals["rev"]))
#     
#     # continuous color ramp
#     validate(
#       need(input$sel_MapScore[1] - as.numeric(binvals["xmin"]) > 0, message = FALSE),
#       need(as.numeric(binvals["xmax"]) - input$sel_MapScore[2] > 0, message = FALSE))
#     rc1 <- colorRampPalette(colors = ColorScheme[1:2], bias = 5)((input$sel_MapScore[1] - as.numeric(binvals["xmin"]))/as.numeric(binvals["xstep"])) # vector of color for values smaller than first cut
#     rc2 <- colorRampPalette(colors = ColorScheme[2:3], bias = 5)((as.numeric(binvals["xmax"]) - input$sel_MapScore[2])/as.numeric(binvals["xstep"]))
#     pal_cont <- colorNumeric(c(rc1, rc2), domain = c(as.numeric(binvals["xmin"]), as.numeric(binvals["xmax"])), reverse = as.logical(binvals["rev"]))
#     
#     if(input$sel_ColorType=="score") {
#       basemap %>%
#         addCircleMarkers(lng = ~Longitude, lat = ~Latitude, opacity = 1, color = ~pal_bins(Metric), radius = 6, fillOpacity = ~ifelse(Metric==0, 0.2, 1), fill = TRUE, popup = ~Poptext) %>%
#         addLegend(position = "bottomright", pal = pal_bins, values = c(as.numeric(binvals["xmin"]), as.numeric(binvals["xmax"])), title = as.character(binvals["title"]), opacity = 1)
#     } else {
#       if(input$sel_ColorType=="cont") {
#       basemap %>%
#         addCircleMarkers(lng = ~Longitude, lat = ~Latitude, opacity = 1, color = ~pal_cont(Metric), radius = 6, fillOpacity = ~ifelse(Metric==0, 0.2, 1), fill = TRUE, popup = ~Poptext) %>%
#         addLegend(position = "bottomright", pal = pal_cont, values = c(as.numeric(binvals["xmin"]), as.numeric(binvals["xmax"])), title = as.character(binvals["title"]), opacity = 1)
#       }
#     }
#   }
#   }
# })
# leafletOutput('vegmap', height=600)
```